---
title: "Xiong_week_07"
author: "Xing Xiong"
date: "2016å¹?11æœ?7æ—?"
output: html_document
---

Read the data first and do cleaning.If the value of Year is like "XX-XX",I select the year which is infront of the hyphen.
```{r}
library(tidyverse)
library(stringr)
health <- read_csv("C:/Users/Administrator/Desktop/wrangling hw/Xiong/xmart.csv")
colnames(health) <- c("Country","Year","MMRatio","SKpersonnel")
health$MMRatio <- str_replace_all(health$MMRatio," ","")
health$lower_bound <- str_extract(health$MMRatio , "\\[[0-9]+")
health$upper_bound <- str_extract(health$MMRatio , "[0-9]+\\]")
health$MMRatio <- str_extract(health$MMRatio , "[0-9]+")
health$lower_bound <- str_replace_all(health$lower_bound , "\\[" , "")
health$upper_bound <- str_replace_all(health$upper_bound , "\\]" , "")
health$Year <- str_extract(health$Year , "[0-9]+")
health$Year <- as.numeric(health$Year)
health$MMRatio <- as.numeric(health$MMRatio)
health$lower_bound <- as.numeric(health$lower_bound)
health$upper_bound <- as.numeric(health$upper_bound)
```


Read another data.Here I use the function is.na to jundge whether the value is NA.Merge the two dataframe and do plots.
```{r}
income <- read_csv("C:/Users/Administrator/Desktop/wrangling hw/Xiong/WHS9_93.csv",skip = 1)
income1 <- income %>% 
gather(2:25 , key = "Year" , value = "income")
income1$income <- str_replace_all(income1$income," ","")
income1$Year <- as.numeric(income1$Year)
final <- merge(health , income1 , by = c("Country"="Country" , "Year"="Year"), all=TRUE)
final <- filter(final,income != "NA")
FINAL <- final[!(is.na(final$MMRatio)) | !(is.na(final$SKpersonnel)),]
plot1 <- ggplot(data = FINAL, aes(x = income , y = MMRatio ,color = Year)) + geom_point()
plot1
plot2 <- ggplot(data = FINAL, aes(x = income , y = SKpersonnel ,color = Year)) + geom_point()
plot2
```

Save the data into my selected file with the name I choose. 
```{r}
write.csv(FINAL,file="C:/Users/Administrator/Desktop/wrangling hw/Xiong/data.csv")
```

First,rank the value of the year in order to select the most recent one.And then form a subset which includes columns we want for the plot.Use function tolower to change the first letter of each country into lower-case letter.Then do the plot. 
```{r}
library(choroplethr)
data1 <- FINAL %>% group_by(Country) %>% mutate(Rank = min_rank(Year)) %>% filter(Year == max(Year))
forplot <- select(data1,Country,MMRatio)
colnames(forplot) <- c("region","value")
forplot$region <- tolower(forplot$region)
plot3 <- country_choropleth(forplot , "Maternal Mortality Ratio" )
plot3
```

Here I have a small question.When I first drew the plot2,R gave me a plot with colorful points.But when I ran the R markdown at last,R gave me a plot with drak colors just shown above.I tried to draw the beautiful plot once again but I failed .Why?